### 2021-05-27 thesis/tex/sterileResults.tex
update

\section{$\chi^2$}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ij} \frac{\left(N^\text{th}-N^\text{data}\right)_{ij}^{2}}
    {\left(\sigma^\text{data}_{ij}\right)^{2} + \left(\sigma^\text{syst}_{ij}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm[41], \theta_{24}\}$, the penalty terms $\alpha$ and $\beta$.
$N_{ij}^\text{th}$ is the expected number of events from theory, and $N_{ij}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ij}^\text{data} = \sqrt{N_{ij}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
\end{align}
with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}. Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

\end{document}

>>>>

\section{$\chi^2$ minimization}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta)=\sum_{ij} \frac{\left(N^\text{th}-N^\text{data}\right)_{ij}^{2}}
    {\left(\sigma^\text{data}_{ij}\right)^{2} + \left(\sigma^\text{syst}_{ij}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm[41], \theta_{24}\}$, the penalty terms $\alpha$ and $\beta$.
$N_{ij}^\text{th}$ is the expected number of events from theory, and $N_{ij}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ij}^\text{data} = \sqrt{N_{ij}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ij} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ij}(\hat{\theta})\,,
\end{align}
with $N_{ij}(\hat{\theta})$ from Eq.~\ref{eq:Nth}. Here, the term $ \beta (0.5 + \zreco_i )$ allows the event distribution to rotate with angle $\beta$ around the median zenith angle of $\zreco = -0.5$.
We also have an uncorrelated systematic error $\sigma_{ijk}^\text{syst}$. We set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$, where $f$ is a percentage of our own choosing,
typically a value between 0 and 20 \%.

The minimization of Eq.~\ref{eq:chisq} simply returns a value for each set of model parameters. We use this value to quantify to what extent
our theoretical simulations $N^\text{th}_{ij}$ agree with the data $N^\text{data}_{ij}$ within the error bounds provided by $\sigma_a,\sigma_b,$ and $f$.
We then select the set of $\chi^2$ values which are the smallest and our allowed parameters are then their associated $\hat{\theta}$.
From the $\chi^2$-distribution, one can show that the $90\%$ confidence level has a value of $2.71$ for two degrees of freedom. When slicing through the 
two-dimensional grid of $\chi^2$ at this level, we then obtain a contour plot that tells us what regions are within our $90 \%$ and what regions are not.

Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
\end{document}
